Toronto Beach Data

### 2024-09-27 paper/paper.qmd
Added Summarise Statistics to Appendix

>>>>

## Summary Statistics of the Data

The summary statistics provides key statistical insights into the environmental variables analyzed at Toronto beaches. For each variable, the summarize tables (@tbl-summarise-air, @tbl-summarise-water, and @tbl-summarise-fowl) reports the mean, median, variance, minimum value, maximum value, and interquartile range of those vairables, offering a concise overview of range, central tendencies, and variability in the data.

```{r}
#| label: tbl-summarise-air
#| tbl-cap: Summarise Statistics of Air Temperatures
#| echo: false
#| warning: false
#| message: false

summarise_air_temp <- data |>
  summarise(Mean = mean(air_temp),
            Median = median(air_temp),
            Variance = var(air_temp),
            Min = min(air_temp),
            Max = max(air_temp),
            IQR = IQR(air_temp)
  )
kable(summarise_air_temp, format = "markdown")
```

```{r}
#| label: tbl-summarise-water
#| tbl-cap: Summarise Statistics of Water Temperatures
#| echo: false
#| warning: false
#| message: false

summarise_water_temp <- data |>
  summarise(Mean = mean(water_temp),
            Median = median(water_temp),
            Variance = var(water_temp),
            Min = min(water_temp),
            Max = max(water_temp),
            IQR = IQR(water_temp)
  )
kable(summarise_water_temp, format = "markdown")
```

```{r}
#| label: tbl-summarise-fowl
#| tbl-cap: Summarise Statistics of Waterfowl Observations
#| echo: false
#| warning: false
#| message: false

summarise_water_fowl <- data |>
  summarise(Mean = mean(water_fowl),
            Median = median(water_fowl),
            Variance = var(water_fowl),
            Min = min(water_fowl),
            Max = max(water_fowl),
            IQR = IQR(water_fowl)
  )
kable(summarise_water_fowl, format = "markdown")
```
